A Survey of Physical Design Techniques of Information Systems

### 2010-07-24 trunk/cs848-db/Paper.tex

\section{Open Problems in Physical Database Design}
\label{SEC-OPEN}

>>>>

\section{Open Research Problems in Physical Database Design}
\label{SEC-OPEN}

Choosing which indexes to create, which views to materialize, and how to partition data are hard choices. They are highly dependent on the schema used as well
as the query workload. The number of combinations of choices that can be made is very large making this task quite tedious and difficult for database
administrators. Accordingly, researchers have been inclined to find ways to automate these decisions. There were many early research efforts done in this
area(E.g.~\cite{finkelstein1988physical, hammer76selec, frank1992selec, chaudhuri1997overview, schiefer1999db2, valentin2000select}), but most of these efforts
focused on having a static workload. Accordingly, research shifted to more dynamic ways to automate physical design. Initial attempts used an dynamic, on-line
approaches(E.g.~\cite{bruno2007online, sattler2003, schnaitter2007}) where they observed the changes in the workload and adjusted the design accordingly while
attempting to predict future behavior based on the observed behavior. To avoid the problems of on-line design, researchers are also currently looking at how to
perform this dynamic physical design off-line (E.g. ~\cite{hannes2008,agrawal2006}).

A second question is how to characterize
scenarios or classes of workloads for which constrained dynamic
physical designs will be beneficial.

Similarly, IBM~\cite{} suggested a similar technique for their database with some changes such as selecting the order of
columns within an index based on the order in which the query optimizer evaluates the predicates.
